Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-08 analysis.qmd

```{r, echo= FALSE, warning = FALSE, message=FALSE}
library("dplyr")
library(mice)
library(sjlabelled)
library(tidyverse)
library("modelsummary")
```

@@

#print(colnames(combined))
reduced_model <- lm(Life.Expectancy ~ Residential.Segregation.Index + X..Limited.Access.to.Healthy.Foods, data = combined)

@@

```{r}
#Variance Inflaction Factor (VIF)
library(car)
vif(mlrmodel)
```

>>>>

```{r, echo= FALSE, warning = FALSE, message=FALSE}
library("dplyr")
library(mice)
library(sjlabelled)
library(tidyverse)
library("modelsummary")
library(car)
```

@@

reduced_model <- lm(Life.Expectancy ~ Residential.Segregation.Index + X..Limited.Access.to.Healthy.Foods, data = combined)

@@

```{r}
#Variance Inflaction Factor (VIF)

vif(mlrmodel)
```
